On Misuses of the Kolmogorov--Smirnov Test for One Sample Goodness-of-Fit

### 2022-04-29 Manuscript/manuscript.tex
updates to fitted+dependence section and conclustion

Figure~\ref{fig:hist_ar1_FD} shows the results of our simulation on data 
simulated from an AR(1) process. The ``super naive" method is the resulting 
p-values when you naively use fitted parameters while ignoring dependence in the
data. The ``naive parametric" plot is the result of applying parametric 
bootstrap to correct for fitted parameters while ignoring potential dependence. 
Of course, the "copula" plot applies the fix for both assumptions. The results 
show that copula remedy generates uniform p-values and restores the power of the
KS test.

@@

The copula fix is not a complete solution, because regardless of the true dependence in the data
we assume an AR(1) model by taking the lag-1 sample auto-spearman rho. However, we can 
show that as long as the AR(1) assumption is a close approximation, the correction still restores power to the test.
Figure~\ref{fig:hist_ma1_FD} is the procedure performed on data generated from 
an MA(1) model with $\theta = 0.5$. Figure~\ref{fig:hist_arma_FD} displays results with 
data generated from an ARMA(1,1) model with $\psi = 0.5$ and $\theta = 0.3$.

@@

It is also possible to apply our procedure to other distributions. All of the simulations
to this point have been done with standard normal data. The data in Figure~\ref{fig:hist_gamma_FD} 
is generated from $Gamma ~ (3,1)$ with a correlation coefficient of $\rho = 0.5$. Figure~\ref{fig:hist_gev_FD}
shows the procedure applied to data from $GEV ~ (0, 0.2, 1)$ with a correlation coefficient of $\rho = 0.5$.

@@

Where this remedy falls short is when the approximation of an AR(1) dependence 
structure is too inaccurate. An AR(2) model can be used to demonstrate this. For 
an AR(2) model with $\phi = (0.5, 0.3)$, Figure~\ref{fig:hist_ar2_FD} 
displays the results of applying the various remedies. While the remedies 
improve the plot of the p-values in comparison to the naive case, because the 
approximation is not close enough the correction does not work completely.

@@

The KS test has base assumptions that the hypothesized distribution is 
completely specified and the data is independent. When these assumptions are 
violated, the test is no longer accurate and remedies must be performed. In the 
case of fitted parameters, parametric and non-parametric bootstrap can restore 
the power of the test. A bias correction is required if the non-parametric form 
is used \citep{Babu}. In the case of dependent data, a procedure using bootstrap 
with copulas to model dependency shows positive results. When both assumptions 
are violated, that is the case where the data has dependence and parameters must 
be fitted, the copula remedy also shows positive results. The tests were 
performed on simulated data from a standard normal distribution, though also 
appear effective against other distributions such as gamma and gev. The copula 
remedy is not a complete solution. Regardless of the true dependence, we use an 
AR(1) model. Therefore, if the AR(1) model is a close approximation of the truth, 
the fix can work. However, in cases such as AR-2, the approximation too far and 
the fix does not completely restore power.

>>>>

Figure~\ref{fig:hist_ar1_FD} shows the results of our simulation on data 
simulated from an AR(1) process. As should be expected, naively fitting 
parameters while providing no adjustment for dependent data invalidates the KS 
test. As well, only using the parametric bootstrap remedy for fitted parameters 
from Section~\ref{sec:fitted} seems to provide weaker results than the 
copula remedy presented above. The results show that copula remedy generates 
uniform p-values and restores the power of the KS test.

@@

Similar to Section~\ref{sec:dependence}, the copula fix is not a complete 
solution. Regardless of the true dependence in the data we assume an AR(1) 
dependence structure by taking the lag-1 sample auto-spearman rho. However, we 
can show that as long as the AR(1) assumption is a close approximation, the 
correction still provides a reasonable approximation that can be useful for 
practical purposes. Figure~\ref{fig:hist_ma1_arma_ar2_FD} shows the results of the 
procedure performed on data generated with dependence structures of  MA(1), 
ARMA(1, 1), and AR(2). Naively fitting parameters and not adjusting for 
dependence clearly deviates from a uniform distribution of p-values. Parametric 
bootstrap provides some correction but does not account for depedence, so 
therefore the results of the copula remedy are more accurate and favorable.
In the case of MA(1) and ARMA(1, 1), the true dependence appears close enough 
to our assumption of AR(1) that the results are reasonable. AR(2) however
appears to be just far enough from our assumption, showing a limitation of the 
procedure.

@@

It is also possible to apply our procedure to other families of distributions. 
The data in Figure~\ref{fig:hist_gamma_gev_FD} is generated from the gamma and 
generalized extreme value distributions. The results are favorable and show that 
the procedure outlined as a fix for fitted parameters and spatially dependent 
can be adapted for various families of distributions.

@@

@@

The KS test has base assumptions that the hypothesized distribution is 
completely specified and the data is independent. When these assumptions are 
violated, the test is no longer accurate and remedies must be performed. In the 
case of fitted parameters, parametric and non-parametric bootstrap can restore 
the power of the test. A bias correction is required if the non-parametric form 
is used \citep{Babu}. In the case of dependent data, a procedure using bootstrap 
with copulas to model dependency shows positive results. When both assumptions 
are violated, that is the case where the data has dependence and parameters must 
be fitted, an adjusted copula procedure also shows positive results. The tests 
appear effective for a variety of families of distributions. The copula remedy 
is not a complete solution and has limitations. Regardless of the true 
dependence, we assume an AR(1) depedennce structure. Therefore, if the AR(1) 
dependence structure is a close approximation of the truth, the fix can work. 
However, in cases such as AR(2), if the approximation is too far from the true 
depedence structure the fix does not completely restore power As well, tests 
were only performed with the normal copula. It is possible that other copulas
could provide stronger results based on the true dependence of the data.
